---
title: "Using Crosstalk"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{using-crosstalk}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The `rsctable()`, `rscgrid()`, `rscsearch()`, and `rscfilter()`  widgets use
`crosstalk` to facilitate inter-widget communication. In simple cases, passing
identical results from the `content()` tibble is sufficient:

```{r, eval=FALSE}
library(connectwidgets)
library(dplyr)
library(purrr)
library(htmltools)

client <- connect()
all_content <- client %>% content()
some_content <- slice_sample(all_content, prop = .1)

tagList(
  bscols(rscsearch(some_content), rscfilter(some_content)),
  rsctable(some_content)
)
```

For more complicated layouts, you may need to pass your own `crosstalk::SharedData()`
objects to the components.
The following example illustrates using [crosstalk groups](https://rstudio.github.io/crosstalk/using.html#grouping)
and, `dplyr`, and `purrr` to:

- display each content owner's username with a level 4 heading
- display an `rscgrid()` of each content owner's items
- enable search across all the card grids


```{r, eval=FALSE}
some_content_xfilter <- crosstalk::SharedData$new(
  some_content,
  group = "xfilter"
  )

rsc_content_filtered_shared <-
  some_content %>%
  group_nest(owner_username, .key = "content_df", keep = TRUE)

div(
  h3("Grouped Grids by Owner", class = "text-center"),
  crosstalk::filter_select(
    "owner_filter",
    label = "Select owners:",
    group = "xfilter",
    multiple = TRUE,
    sharedData = some_content_xfilter
  ),
  pmap(
    rsc_content_filtered_shared,
    {
      ~ tagList(
        h4(..1),
        rscgrid(crosstalk::SharedData$new(..2, group = "xfilter"))
      )
    }
  )
)
```

